Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2012-03-07 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2012:03:05	15:17:06	(Mon 5.Mar)
la2pdf commit - 2012:03:05	15:47:24	(Mon 5.Mar)
la2pdf commit - 2012:03:05	16:19:35	(Mon 5.Mar)
la2pdf commit - 2012:03:07	11:23:25	(Wed 7.Mar)

% \input{preamble}

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
   \usepackage[dvips]{graphicx}                 % Might not work. Use 'latex' instead of 
   \ifFlatArchive\else                          % 'pdflatex'
      \graphicspath{./gfx/}
   \fi
\else
   \usepackage[dvips]{graphicx}
   \ifFlatArchive\else
      \graphicspath{./gfx/}
   \fi
\fi

@@

\ifTODO
   \setlength{\marginparwidth}{1cm}
%    \setlength{\marginparpush}{1cm}
%    \setlength\marginpar{1.5cm}
   \addtolength\marginparsep{0.1cm}
%    \definecolor{lightblue}{rgb}{0.8,0.8,1}
%    \newlength\textwidthold
%    \setlength\textwidthold{\textwidth}
%    \setlength\textwidth{\columnwidth}
   \usepackage{./todonotes}
%    \setlength\textwidth\textwidthold
\else
   \usepackage[disable]{todonotes} 
\fi

@@

@@

%%%%%%%%%%%%%%%%%%                              ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% DOCUMENT START %
%%%%%%%%%%%%%%%%%%                              ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
  \RequirePackage{layout}  
\begin{document}
\layout
%
\title{Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging}

@@

\IEEEPARstart{A}{daptive} beamformers have only recently been introduced in active sonar imaging.\todo{break at something} This is because , as demo file is intended to serve as a ``starter file''
for IEEE Computer Society journal papers produced under \LaTeX\ using
IEEEtran.cls version 1.7 and later.

@@

% needed in second column of first page if using \IEEEpubid
%\IEEEpubidadjcol

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation Results}
%\label{fig_sim}
%\end{figure}

% Note that IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.
% However, the Computer Society has been known to put floats at the bottom.

@@

>>>>

\ifCLASSINFOpdf
   \usepackage[dvips]{graphicx}                 % Might not work. Use 'latex' instead of 
   \ifFlatArchive\else                          % 'pdflatex'
      \graphicspath{./gfx/}
   \fi
\else
   \usepackage[dvips]{graphicx}
   \ifFlatArchive\else
      \graphicspath{./gfx/}
   \fi
\fi

@@

@@

\newcounter{todoidx}
% \setcounter{todoidx}

\ifTODO
   \definecolor{todobackground}{rgb}{0.95,0.95,0.95}
   \setlength\marginparsep{3pt}
   \setlength\marginparwidth{42pt}
   \newlength\marginparwidthsmall
   \setlength\marginparwidthsmall{\marginparwidth}
   \addtolength\marginparwidthsmall{-7pt}
   \newcommand\todo[1]{%
      \addtocounter{todoidx}{1}%
      {\color{Red}\fbox{\bf\thetodoidx{}}}%
      \marginpar{%
         {\vspace*{-10pt}\color{Red}\fbox{\bf\thetodoidx{}}}\\%
         \fcolorbox{red}{todobackground}{\parbox{\marginparwidthsmall}{#1}}}}
\else
%    \usepackage[disable]{./todonotes} 
   \newcommand\todo[1]{}
\fi

@@

%%%%%%%%%%%%%%%%%%                              ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% DOCUMENT START %
%%%%%%%%%%%%%%%%%%                              ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\begin{document}

\title{Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging}

@@

\IEEEPARstart{T}{o} form images from a modern phased array sonar system the received waveform is usually recorded, and then processed by a digital beamformer. Estimating one pixel at a time, the beamformer adjusts the arrays spatial response to ensure the maximum gain in the direction of the pixel of interest, while maintaining maximum suppression at all other angles.

The imaging capabilities of a modern phased array sonar system depend on physical attributes such element response and array geometry, the transmitted signal, as well as the beamforming method being used on transmission and reception. Beamforming is the concept of applying delays and weights to the sensors channels to steer the arrays response to points of interest.

\begin{itemize}
\item Why beamforming?
\item Adaptive beamformers
\item Challenges in active sonar systems. Correlated noise, robustification kills the adaptive potential. Quite computationally intensive.
\item LCA
\end{itemize}

, and maximum suppression of while ensuring that the beamformer digitally  before each of the pixels are estimated one at a time. The resolution and contrast of such a system will depend on the systems spatial response, which ideally should be narrow  be very sharp in the desired direction its ability to achieve  fundamental principle of forming a sonar image is to record the received wavefield,

image quality of a phased array sonar imaging systems depend on  the choice of weights to apply to each of the sensors are crucial.

A modern phased array imaging system may be thought of as a spatial filter. To achieve the best possible performance, the

resolution and contrast

Adaptive beamformers have only recently been introduced in active sonar imaging. For a while they were considered unsuited for this purpose because the backscattered signal is largely correlated with the

@@

%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation Results}
%\label{fig_sim}
%\end{figure}

@@

\bibliography{../../Library/library}
